Gammapy: A Python package for gamma-ray astronomy

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Cosimo Nigro <cosimonigro2@gmail.com>

\subsection{Broadband SED Modeling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes users can also fit
astrophysical spectral models to \gammaray data. In \gammaray
astronomy one typically observes two radiation production
mechanisms, the so-called hadronic and leptonic scenarios.
There are mutiple Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
Tyically those emission models predict broadband emission from
radio waves up to the very high-energy \gammaray range.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} that allows
users to wrap a given astrophysical emission model from the
"naima" package and fit it directly to \gammaray data.

>>>>

\subsection{Broadband SED Modeling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes, users can also fit
astrophysical spectral models to \gammaray data. In \gammaray
astronomy one typically observes two radiation production
mechanisms, the so-called hadronic and leptonic scenarios.
There are mutiple Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are  \cite{agnpy}, \cite{naima}, \cite{jetset} or \cite{gamera}.
Tyically those emission models predict broadband emission from
radio waves up to the very high-energy \gammaray range.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} that allows
users to wrap a given astrophysical emission model from the
"naima" package and fit it directly to \gammaray data.
